Report

### 2023-05-26 implementation/Report.Rmd
updates

```{r setup, include=FALSE}
## Global options
library(reticulate)
library(knitr)
library(flexdashboard)
library(scales)
library(here)
library(tidyverse)
library(readr)
library(plotly)
library(tidyverse)
knitr::opts_chunk$set(cache = TRUE)
source(here('modules','data_funcs.R'))

@@

@@

@@

@@

>>>>

```{r setup, include=FALSE}
## Global options
library(reticulate)
library(knitr)
library(flexdashboard)
library(scales)
library(here)
library(tidyverse)
library(readr)
library(plotly)
library(tidyverse)
library(here)
knitr::opts_chunk$set(cache = TRUE)
source(here('modules','data_funcs.R'))

@@

Additionally the far right graph shows the approximate decision making.

Policy:

* MDP will schedule into the first 2 days only. 
* In this approximate order:

  * Surgery 6, Complexity 1
  * Surgery 1, Complexity 1
  * Surgery 6, Complexity 2
  * Surgery 4, Complexity 2
  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2

@@

Policy:

* MDP will schedule into the first 2 days only. 
* In this approximate order:

  * Surgery 6, Complexity 1
  * Surgery 6, Complexity 2
  * Surgery 1, Complexity 1
  * Surgery 4, Complexity 2
  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2

@@

Policy:

* MDP will schedule S6 and S1C1 into the first 2 days only. S4 and S1C2 will be scheduled into the entire planning horizon.
* In this approximate order:

  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2
  * Surgery 4, Complexity 2
  * Surgery 6, Complexity 1
  * Surgery 6, Complexity 2
  * Surgery 1, Complexity 1

@@

Policy:

* MDP will schedule S6 and S1C1 into the first 2 days only. S4 and S1C2 will be scheduled into the entire planning horizon.
* In this approximate order:

  * Surgery 4, Complexity 1 / Surgery 1, Complexity 2
  * Surgery 4, Complexity 2
  * Surgery 6, Complexity 1
  * Surgery 1, Complexity 1
  * Surgery 6, Complexity 2
